---
title: "AN 588 Week 3"
author: "Erin Anderson"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highight: github
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CHALLENGES 

What you learned from running their Original Homework Code that helped improve your own code.

What you did in your own code that might help to improve theirs.

What challenges, if any, you both faced in your code that could not be helped by comparison.

Whether the annotation/commenting on your peer’s Original Homework Code is readable and interpretable to you, and if not then how it could be improved.

## What is the probability she will hear more than 8 calls during any given session?
```{r 8 or more calls, include=TRUE}
eight_calls <- ppois(q = 8, lambda = 15, upper.tri(TRUE))
eight_calls
```
## Probability of no calls
```{r no calls, include=TRUE}
no_calls <- dpois(x = 0, lambda =15)
no_calls
```
## Probability of exactly 3 calls
```{r exactly 3, include=TRUE}
three_calls <- dpois(x = 3, lambda =15)
three_calls
```
## Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r Poisson mass function, include=TRUE}
x <- 0:30
l = 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "Number of Calls", ylab = "Probability", main = "Probability Mass Function")
```

## Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions)
```{r simulate 104 results, include=TRUE}
two_years <- rpois(104, lambda =15)
two_years
```

## Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30
```{r final plot, include=TRUE}
hist(two_years, probability = TRUE, main = "Two Years of Data",
    xlab = "Number of Calls", ylab = "probability", xlim = c(0,30))
```